### 2022-02-24 paper.Rmd
removed unnecessary abbreviation

First, I generated 10,000 data sets which were subsequently processed by to the three competing anticlustering methods. The following properties were determined randomly for each data set: (a) the sample size $N$ varied between 24 and 300 with intermediate steps of 12 so that each data set could be split evenly into $K = 2$, $3$, and $4$ groups; (b) the number of features $M$ varied between 1 and 10; (c) the distribution of features was randomly determined to be either (i) uniform in [0, 1], (ii) a standard normal distribution with *M* = 0 and *SD* = 1, or (iii) a wider normal distribution with *M* = 0 and *SD* = 2. For a given data set, all $M$ features were independently sampled from the given distribution and no correlations were assumed between features. All three anticlustering methods were applied to each of the 10,000 data sets using $K = 2$, $K = 3$ and $K = 4$. Groups sizes were always equal.

>>>>

First, I generated 10,000 data sets which were subsequently processed by to the three competing anticlustering methods. The following properties were determined randomly for each data set: (a) the sample size $N$ varied between 24 and 300 with intermediate steps of 12 so that each data set could be split evenly into $K = 2$, $3$, and $4$ groups; (b) the number of features varied between 1 and 10; (c) the distribution of features was randomly determined to be either (i) uniform in [0, 1], (ii) a standard normal distribution with *M* = 0 and *SD* = 1, or (iii) a wider normal distribution with *M* = 0 and *SD* = 2. For a given data set, all $M$ features were independently sampled from the given distribution and no correlations were assumed between features. All three anticlustering methods were applied to each of the 10,000 data sets using $K = 2$, $K = 3$ and $K = 4$. Groups sizes were always equal.
